\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-09-21 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex

\begin{abstract}
This paper investigates the pattern of international transport costs over time, using information contained in the US imports flows from 1974 to 2019. First, we document the importance of the per-unit component of transport costs. It represents between one-third and one-half of overall transport costs. Second, allowing for time-varying per-unit costs, we find that the downward trend in international transport costs comes from the reduction in ``pure'' transport costs over time, with trade composition effects playing a minor role. In both aspects, our results point to the importance of the additive component in accounting for international transport costs. \textbf{A REPRENDRE - BIG PICTURE}
\end{abstract}

@@

\noindent \emph{JEL classification}: F10, N70, R40 \\
\noindent \emph{Keywords}: Transport costs estimates, non-linear econometrics, period 1974-2019, additive costs, trade composition effects

@@

Our results may be summarized in two main new findings.
First, additive transport costs are quantitatively sizable.
On average over 1974-2019, the additive cost is estimated to be 1.7\% and 2.8\% of the export price in air and vessel transport respectively (at the 3-digit classification level). This is slightly lower than our estimates for the ad-valorem component (2.4\% and 3\% for air/vessel respectively on average over the period).
Put differently, additive costs represent on average between 30 and 45\% of the overall transport costs. To the best of our knowledge, our paper is the first to provide such an extensive quantitative measure of both ad-valorem and additive costs in total transport costs.
This represents a valuable insight for calibrating related international trade or business cycle models.
We also provide an empirical assessment of what standard international trade models lose by skipping additive transport costs.
Quantitatively, the omission of the additive term leads to overestimate the ad-valorem component by a factor around 2. Further, the goodness of fit is systematically better when the additive component is included in the regression, even when taking into account the removed degree of freedom.\smallskip

\textbf{A REPRENDRE - BIG PICTURE EN DEUX POINTS }

Second, we find that the main source of the downward trend in overall transport costs comes mainly from the reduction of transport cost \textit{per se}, by roughly \textbf{50\% in air shipping and 60\% in vessel shipping over 1974-2019}.\footnote{Throughout the paper, we refer to ``pure'' or ``\textit{per se}'' transport costs changes as the changes over time in the transport costs for a given product/country partner, ie excluding trade composition effects (i.e. changes over time in the baskets of imported goods and/or the origin countries).} Specifically, trade composition effects have only limited influence in accounting for the downward trend of international transport costs, and when they matter (in maritime transport), composition effects amplify the reduction of pure transport costs. This contrasts with the conclusion obtained by \cite{hummels2007} yet also on US import flows.%\footnote{Both Hummel's and our's databases come from the US Bureau of Census's import flows database, with two differences yet. First, we consider a larger period of time, spanning from 1974 (as in \cite{hummels2007}) to 2019 (while he stops in 2004). Second, while Hummels considers products at the 5-digit classification level, we are able to exploit heterogeneity in the data at the much more disaggregated HS-10 level for the vast majority of the period (1989-2019). For the period 1974-1988, we rely on Hummel's original database with a 5-digit product classification level.}
\cite{hummels2007} finds that total transport costs have decreased in both air and maritime shipment, but less so than ``pure'' transport costs, because trade composition effects have partly offset the pure transport costs decrease, thereby attenuating the overall downward trend in transport costs. Importantly, we show that the difference of results can be attributed to the new method of modeling the additive component that we offer. Allowing the share of additive costs to vary across time, products and country partners (rather than being constant as in \citealp{hummels2007}), turn out to be key in the decomposition of underlying sources of the decrease of overall transport costs observed over the period.

@@

Closely related to our paper is the work by \cite{Irrazabal_2015}, which develops a structural framework for inferring relative additive trade costs from firm-level trade data.
Implementing their methodology on Norwegian firm-level export data for the year 2004, they find that, for the median shipment, additive costs (in Norwegian crowns) amount to 6\% of the export price multiplied by the ad-valorem cost (also expressed in Norwegian crowns).
Our results share in common with \cite{Irrazabal_2015} the important role of the additive component of international trade costs.
Yet, our paper complements their findings in two main respects.
First, while our study covers a narrower set of trade costs focused on transport costs, their data and their empirical approach only allows the identification of \textbf{the ratio of the additive cost to the export price multiplied by the ad-valorem cost LE DIRE PLUS SIMPLEMENT}; by contrast, our estimation strategy enables us to estimate each value of the ad-valorem and the additive costs independently from the other. From this, we can rebuild the ratio in similar terms to them, thereby gaining in generality in this respect. \textbf{A DEVELOPPER A MINIMA SUR LES IMPLICATIONS EN TERMES DE MODELISATION?}
While \cite{Irrazabal_2015} find that, for an export price multiplied by the ad-valorem cost of 100 USD, 6 USD are paid in additive trade costs, our results point to a value paid in additive transport costs of 2.8 USD for maritime shipping and 1.5 USD for air transport for 2004.
This comparison of results suggests that between a quarter and a half of the additive trade costs are attributable to the transport sector (depending on the transport mode).%JH : these results should not change, they are for 2004.
Second, we exploit exhaustive information about the imports flows of the US over a wide time-span from 1974 to 2019.
In this respect, our results deliver a broader view of the magnitude of additive costs in international trade over time.
In particular, we show that the modeling of additive costs is of critical importance in determining the underlying sources of the trends patterns of international transport costs observed over the last fifty years.

%\textbf{Big Picture}.
Our results are robust to a range of robustness checks, including the use of instrumental variables and more disaggregated data at the SITC 4 or HS10 levels. They have important implications for both international trade and international macroeconomics models. \textbf{Parler des effets de composition comme une des implications}. Beyond the positive aspect, some recent papers also point out the normative implications of additive trade costs. \cite{sorensen2014} thus analytically shows that important welfare gains can be achieved by reducing additive trade costs. Not much progress has yet been made in quantifying such gains, one potential reason being the lack of an empirical characterization of the additive component of trade costs (the one exception being \citealp{Irrazabal_2015}). The quantitative results we provide in the paper allow making one step in filling that gap. %\footnote{ \cite{sorensen2014} extends \cite{melitz}'s seminal model of international trade by including additive trade costs, in addition to the ad-valorem component. A key analytical result is that the welfare gain from a reduction in trade barriers is higher for a decrease in additive costs than a decrease in ad-valorem costs, due to the alteration of relative prices in a heterogeneous-firms trade framework. This is confirmed by \cite{Irrazabal_2015}.}
 %On the same toke, as additive costs distort relative prices, they are very likely to affect the international transmission of shocks in international business cycles models.

More precisely, we use our estimates of multiplicative and additive costs for the years 1974 and 2019 to implement several comparative static exercises investigating the different welfare consequences of alterations to multiplicative and additive costs. For a given decrease in transport costs, welfare gains are around 50\% higher when the underlying framework allows for additive costs - which, in practice, concentrate the major part of transport costs decrease over the period. In addition, we also assess how the latter results are distorted by changes in sunk costs of exports (i.e., increase in the share of exporting firms). Welfare gains are proportionally amplified, with again an additional premium coming from the decrease of additive costs.

@@

The remainder of the paper is built as follows. The following section presents the data and the baseline empirical model used to estimate the values of international transport costs. Section \ref{sec:basic_results} reports the later on a yearly basis throughout the period 1974-2019 by transport mode, explicitly distinguishing between the additive and the ad-valorem components and providing several important robustness checks of our results. In particular, section \ref{sec:basic_results} reports the mean values of the transport costs estimated over the period (by transport mode). The two following sections take stock of those results to draw implications for two important debates in economic analysis. In section \ref{sec:results_trends}, we offer new insights on the origins of the decrease of transport costs over time, by providing a decomposition of the transport costs trend patterns, between what arises from changes in the trade composition (by product and/or partner country), and what is attributable to changes in transport costs \textit{per se}. Section\ref{sec:theory} implements several theory-based calibration exercises to investigate the different welfare consequences of alterations to multiplicative and additive costs, and section \ref{sec:conclu} concludes.

@@

\begin{table}[htbp]
 \centering
\caption{Transport costs estimates: summary} \vspace{5mm} \label{tab:summary_results}
	\input{Table1.tex}
		\begin{tablenotes}
		\tiny
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
		\item 1989 trade by air is excluded
		%\item The additive term is expressed in fraction of fas price.
		\item For the  4-digit model, statistics for observed data have been calculated for the same set of years as used for estimation, i.e.
		1974, 1981, 1989, 2001, 2009, 2013, 2017 and 2019
		\item \textbf{Model (a): With ad-valorem transport costs only}
		\item \textbf{Model (b): With additive and ad-valorem transport costs}
	\end{tablenotes}
\end{table}

@@

As shown in Figure \ref{fig:Trends_in_TC}, both air and vessel shipping exhibit a downward trend in overall transport costs since 1974, by \textbf{ACTUALISER LES CHIFFRES -2.1\% per year for mean air transport costs and -2.0\% per year XXX JH à GD : STP, refaire tourner la regression sous-jacente} for mean vessel transport costs, implying a 50\% decrease in air and a 60\% decrease in vessel over the period.\footnote{One may be puzzled by the high magnitude of estimates for the beginning of the period (until 1980 approximately) for vessel transport.
\cite{hummels2007} finds similar outcomes on tramp prices indexes, and suggests the oil shock as a likely culprit, in a context where technological progress was quicker in aviation than in vessel, allowing a better dampening of oil shocks on air freight rates.
In a related manner, one may worry that the strong decrease in transport costs documented in Figure \ref{fig:Trends_in_TC} springs from high oil-shock-related transport costs in 1974. However, computing the time trends from 1980 does not dramatically change the picture.
The yearly trend from 1980 is -2\% for mean air transport costs and -1.6\% for mean vessel transport costs.
We thus choose to exploit the whole time dimension of our database by taking 1974 as starting date of our time-trend analysis.} Using US data, \cite{Hummels_1999} found that overall transport cost declined from 6\% to 4\% of the import value between 1974 and 1996.
For the same years, we obtain a total decrease from 6.9\% to 4.2\% in terms of the export price, on average for air shipping, and from 9.8\% to 4.8\% for ocean shipping. Overall, our results display trends confirm and extend those reported by \cite{Hummels_1999} up to the very recent years.\smallskip

@@

Current data are available at the 10-digit level for products (HS10).
Theoretically, they should be available from 1989.
But because of the COVID situation, it was only possible to get 1997-1999 and 2001-2019.
Yet, as Table \ref{tab:baseline10} and 	Figure \ref{fig:robustness_to_agregation} show, the results are similar when using 10-digit product and 5-digit products.

\begin{table}[htbp]
	\centering
	\caption{Transport costs estimates: robustess to agregation} \vspace{5mm} \label{tab:baseline10}
	\input{Table_baseline10.tex}
	\begin{tablenotes}
		\tiny
		\item Statistics for 1997-1999 and 2002-2019
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
		\item \textbf{Model (a): With ad-valorem transport costs only}
		\item \textbf{Model (b): With additive and ad-valorem transport costs}
	\end{tablenotes}
\end{table}

\begin{figure}[htbp]
	\caption{Transport cost time trends: robustness to agregation}
	\label{fig:robustness_to_agregation}
	\begin{center}
		\includegraphics[height=8cm]{scatter_chronology_baseline_baseline10.png}
	\end{center}
\end{figure}

@@

Based on the above results, we provide a decomposition of the transport costs trends between the trade composition effects and the ``pure'' transport costs time trends, which explicitly takes into account the varying share of additive costs over time, country partner and product.\footnote{See Appendix \ref{app:compare_Hummels} for a detailed exposition of our method and a comparison of Hummel's (2007) methodology.} An important contribution of the paper is to show the crucial role of this (empirically relevant) assumption, as it notably modifies the conclusions relative to the role of trade composition effects.
We start with the presentation of our estimation strategy before turning to the results.\smallskip

@@

In this section, we explore the implications of our empirical results on theoretical grounds. While the whole bulk of the trade literature investigates the role of trade costs modelled as ad-valorem costs (e.g., iceberg trade costs), not much is said about the role of the additive component. One potential explanation is the lack of empirical estimates about the size of additive costs. Our results may thus usefully palliate this limitation. Specifically, we make use of our empirical results to investigate the welfare consequences of a reduction in international transport costs, when such a reduction also occurs through a reduction in the additive component. \cite{Irrazabal_2015}, \cite{sorensen2014} and \cite{Lashkaripour_JIE2020} have preceded us on this issue. We differentiate from them in the following way. \cite{sorensen2014} explores the welfare effects of a trade costs reduction depending on whether they are either fully ad-valorem or fully additive. In contrast, we provide a quantification of such welfare gains, as in \cite{Irrazabal_2015} or \cite{Lashkaripour_JIE2020}. To do so, we rely on our empirical estimates of the transport costs values, that induce a combined decrease in both the ad-valorem and the additive components over the last decades. In a partial-equilibrium model with perfect competition, \cite{Lashkaripour_JIE2020} obtains that welfare gains are not substantially different whether the transport cost decrease implies an additive component or not. This stands in contrast with the conclusion reached by \cite{sorensen2014} (analytically) and \cite{Irrazabal_2015} (quantitatively) in M\'{e}litz' type models. Anticipating on our results, we also share the result, that the transport cost reduction implies substantially larger welfare gains when they are achieved through a reduction in the additive component. As first explanation, it should be noted that, in \cite{Lashkaripour_JIE2020}'s paper, the case with additive costs relies on a share of additive costs that remains negligible. In this context, one might expect that whether additive costs are present or not makes little difference. As underlined by \cite{Lashkaripour_JIE2020}, a second explanation may rely on the modeling framework. While \cite{Lashkaripour_JIE2020} models a perfectly competitive model, we as in \cite{sorensen2014} and \cite{Irrazabal_2015} adopt a model with monopolistic competition and firm selection \`{a} la \cite{melitz} or \cite{chaney2008}. In this setting, we show that additive costs do modify the selection of firms on both the domestic and the export markets, e.g the extensive margin of trade, whose role in the welfare gains of trade liberalization lies at the heart of the New Trade models  \`{a} la \cite{melitz}. Put differently, leaving aside the selection issue leads to underestimate the welfare gains that can be achieved by a reduction in the additive component of transport costs.

@@

In line with the literature, we find that trade liberalization induces welfare gains whatever the transport mode (and the associated magnitude of the transport costs decrease). The originality of our results rather dwells on comparing the welfare gains depending on the type of cost reduction. On that side, the welfare gains are higher when the trade cost reduction occurs through a decrease in the additive component. This is consistent with the analytical results of \cite{sorensen2014}, in a different exercise of trade liberalization though. \footnote{\cite{sorensen2014} compares the welfare effect of a trade costs reduction depending whether it is exclusively ad-valorem or exclusively additive, the comparison between both trade cost decreases being a criterion of equal impact on trade openness. Our quantitative model offers a more general and flexible set-up, as we can virtually consider all cases of trade liberalization. Based on our empirical estimates, we compare the effects of the same decrease in overall transport costs depending on 1) whether additive costs are present or not, and 2) when they are present, assuming that the trade cost decrease is achieved by a reduction of both additive and ad-valorem components.} Quantitatively, the welfare gains are sizeable. In our preferred scenario, the reduction variable transport costs generates a relative welfare gain higher by around 1.1 percentage point when such a reduction occurs through the additive component (which accounts for 50 to 60\% of the total cost decrease, depending on the transport mode), rather than when it realizes through a decrease in iceberg costs only (Table \ref{tab:resultats_modele}, panel (1), Column (B) vs (A) for Air, (D) vs (C) for Vessel). \cite{Irrazabal_2015} also quantify the welfare gains of a trade cost decrease in presence of additive costs. In contrast to \cite{Irrazabal_2015} though, our empirical analysis allows us to simulate the effects of the reduction in transport costs actually observed in the data over the period 1974-2019, in all their dimensions (additive and ad-valorem). \smallskip

@@

This paper empirically studies the magnitude of additive costs in international transport costs, by exploiting the differences between the import and the export prices.
Using SITC 3 and 4- digit cif-fas unit values taken from the US import database over 1974-2019, we estimate the two components (additive and ad-valorem) of transport costs, by transport mode (air or ocean).
Two main findings emerge from our results.
First, we provide a quantitative measure of both the additive and the ad-valorem transport costs.
We find that additive costs are quantitatively sizable: They amount to 2.8\% of the export price unit values for ocean shipping, and 1.8\% for air transport.
This is slightly lower that the estimated values for the ad-valorem costs, around  2.5\% (vessel) and 3.2\% (air) as mean values over 1974-2019.
Further, modeling the additive component significantly improves the quality of fit of the regression.
Second, we show the importance of integrating the additive component in accounting for the time trend of international transport costs.
Allowing for a varying share of additive costs in the product/country/time dimension, we find that the decrease of international transport costs observed in the data is mostly attributable to a reduction in the \textit{pure} transport costs, with trade pattern composition effects playing a small role.
If anything, trade composition effects have contributed to amplifying the reduction in the pure transport costs in maritime transport.
In both aspects, our results highlight the importance of the additive component in accounting for international transport costs.

Our results could be extended in two main ways.
On the empirical side, one may want to go deeper into the structural determinants of (pure) transport costs - i.e.
identify the respective roles of handling costs, insurance and freight at the root of the gap between export and import prices.
On the theoretical side, our results can be used to explore the role of additive costs in shaping international trade flows in an international trade theory perspective and in affecting the international transmission of business cycles.
This is left for further research.

>>>>

\begin{abstract}
This paper demonstrates the magnitude and the role of additive international transport costs. Using information contained in the US imports flows from 1974 to 2019, we develop an empirical model that disentangles the ad-valorem and the additive components of international transport costs. As main result, we quantify the importance of the per-unit component of transport costs: It represents between 30\% and 45\% of overall transport costs. We then emphasize the consequences of modelling additive costs, under two different angles. First, modelling time-varying per-unit costs modifies the decomposition of transport costs time trend between the reduction in ``pure'' transport costs and trade composition effects, the latter playing a minor role. Second, we evaluate the normative consequences role of trade liberalization in presence of additive costs. Neglecting the additive component substantially underestimates the welfare gains of the transport cost decrease, by around 1.2 percentage points. In both aspects, our results point to the importance of modelling the additive component of international transport costs.
\end{abstract}

@@

\noindent \emph{JEL classification}: F10, N70, R40 \\
\noindent \emph{Keywords}: Transport costs estimates, non-linear econometrics, period 1974-2019, additive costs, trade composition effects, heterogenous firms

@@

As main result, we show that additive transport costs are quantitatively sizable. On average over 1974-2019, the additive cost is estimated to be 1.7\% and 2.8\% of the export price in air and vessel transport respectively (at the 3-digit classification level). This is slightly lower than our estimates for the ad-valorem component (2.4\% and 3\% for air/vessel respectively on average over the period).
Put differently, additive costs represent on average between 30 and 45\% of the overall transport costs. To the best of our knowledge, our paper is the first to provide such an extensive quantitative measure of both ad-valorem and additive costs in total transport costs.
This represents a valuable insight for calibrating related international trade or business cycle models.
We also provide an empirical assessment of what standard international trade models lose by skipping additive transport costs.
Quantitatively, the omission of the additive term leads to overestimate the ad-valorem component by a factor around 2. Further, the goodness of fit is systematically better when the additive component is included in the regression, even when taking into account the removed degree of freedom.\smallskip

A natural question then emerges: To what extent should we care about additive costs? Our paper answers this question from two different sides.

On the empirical side first, we show the importance of incorporating additive costs in the understanding of the international transport costs decrease observed between 1974 and 2019. Allowing for time-varying per-unit costs, we find that the downward trend in international transport costs comes from the reduction in ``pure'' transport costs over time, by roughly \textbf{50\% in air shipping and 60\% in vessel shipping over 1974-2019}.\footnote{Throughout the paper, we refer to ``pure'' or ``\textit{per se}'' transport costs changes as the changes over time in the transport costs for a given product/country partner, ie excluding trade composition effects (i.e. changes over time in the baskets of imported goods and/or the origin countries).} Trade composition effects have only limited influence in accounting for the downward trend of international transport costs, and when they matter (in maritime transport), composition effects amplify the reduction of pure transport costs, in contrast with the conclusion obtained by \cite{hummels2007} yet also on US import flows.
%\cite{hummels2007} finds that total transport costs have decreased in both air and maritime shipment, but less so than ``pure'' transport costs, because trade composition effects have partly offset the pure transport costs decrease, thereby attenuating the overall downward trend in transport costs. 
Importantly, we show that the difference of results can be attributed to the new method of modeling the additive component that we offer. Allowing the share of additive costs to vary across time, products and country partners (rather than being constant as in \citealp{hummels2007}), turns out to be key in the decomposition of underlying sources of the decrease of overall transport costs observed over the period.\smallskip

We also show the importance of embedding additive costs when assessing the effects of trade liberalization in normative terms. Specifically, we
make use of our empirical results to investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019, contrasting two cases: When this reduction solely occurs through a decrease in the ad-valorem cost, as standardly modelled in New Trade models, versus when it is achieved through a combined reduction in the ad-valorem and the additive components, as quantified by our empirical model. To this aim, we embed additive costs in the canonical \cite{melitz} model. Relying on our empirical estimates of transport costs
over 1974-2019, our preferred scenario shows an extra welfare gain by around 1.2 percentage point when the transport cost decrease encompasses a reduction in its additive component (as we document empirically) relative to a pure ad-valorem reduction. Put differently, neglecting additive costs thus leads to a substantial underestimation of the welfare gains of trade liberalisation.

@@

Closely related to our paper is the work by \cite{Irrazabal_2015}, which develops a structural framework for inferring relative additive trade costs from firm-level trade data.
Implementing their methodology on Norwegian firm-level export data for the year 2004, they find that, for the median shipment, additive costs (in Norwegian crowns) amount to 6\% of the export price multiplied by the ad-valorem cost (also expressed in Norwegian crowns).
Our results share in common with \cite{Irrazabal_2015} the important role of the additive component of international trade costs.
Yet, our paper complements their findings in two main respects.
First, while our study covers a narrower set of trade costs focused on transport costs, their data and their empirical approach only allows the identification of the ratio of the additive cost to the export price multiplied by the ad-valorem cost; by contrast, our estimation strategy enables us to estimate each value of the ad-valorem and the additive costs independently from the other. From this, we can rebuild the ratio in similar terms to them, thereby gaining in generality in this respect. While \cite{Irrazabal_2015} find that, for an export price multiplied by the ad-valorem cost of 100 USD, 6 USD are paid in additive trade costs, our results point to a value paid in additive transport costs of 2.8 USD for maritime shipping and 1.5 USD for air transport for 2004. This comparison of results suggests that between a quarter and a half of the additive trade costs are attributable to the transport sector (depending on the transport mode). %JH : these results should not change, they are for 2004.
Second, we exploit exhaustive information about the imports flows of the US over a wide time-span from 1974 to 2019.
In this respect, our results deliver a broader view of the magnitude of additive costs in international trade over time.
In particular, we show that the modeling of additive costs is of critical importance in determining the underlying sources of the trends patterns of international transport costs observed over the last fifty years.  \smallskip

%\textbf{Big Picture}.
Our results are robust to a range of robustness checks, including the use of instrumental variables and more disaggregated data at the SITC 4 or HS10 levels. They have important implications for both international trade and international macroeconomics models. Some recent papers notably point out the normative implications of additive trade costs. \cite{sorensen2014} analytically shows that important welfare gains can be achieved by reducing additive trade costs. Not much progress has yet been made in quantifying such gains, one potential reason being the lack of an empirical characterization of the additive component of trade costs, the one exception being \citealp{Irrazabal_2015}. In contrast to them, we can exploit the time dimension of our database to quantify the welfare gains of the trade liberalization at stake since 1974, based on our empirical yearly estimates over 1974-2019 of overall transport costs and by sub-component (additive and ad-valorem).\smallskip

@@

The remainder of the paper is built as follows. The following section presents the data and the baseline empirical model used to estimate the values of international transport costs. Section \ref{sec:basic_results} reports the later on a yearly basis throughout the period 1974-2019 by transport mode, explicitly distinguishing between the additive and the ad-valorem components and providing several important robustness checks of our results. In particular, section \ref{sec:basic_results} reports the mean values of the transport costs estimated over the period (by transport mode). The two following sections take stock of those results to draw implications for two important debates in economic analysis. In section \ref{sec:results_trends}, we offer new insights on the origins of the decrease of transport costs over time, by providing a decomposition of the transport costs trend patterns, between what arises from changes in the trade composition (by product and/or partner country), and what is attributable to changes in transport costs \textit{per se}. Section \ref{sec:theory} implements several theory-based calibration exercises to investigate the different welfare consequences of alterations to multiplicative and additive costs. Section \ref{sec:conclu} concludes.

@@

\begin{table}[htbp]
 \centering
\caption{Transport costs estimates: summary} \vspace{5mm} \label{tab:summary_results}
	%\input{Table1.tex}
\input{Table1_reshaped.tex}
		\begin{tablenotes}
		\scriptsize
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
		\item 1989 trade by air is excluded
		%\item The additive term is expressed in fraction of fas price.
		\item For the  4-digit model, statistics for observed data have been calculated for the same set of years as used for estimation, i.e.
		1974, 1981, 1989, 2001, 2009, 2013, 2017 and 2019
		\item \textbf{Model (A): With ad-valorem transport costs only}
		\item \textbf{Model (B): With additive and ad-valorem transport costs}
	\end{tablenotes}
\end{table}

@@

As shown in Figure \ref{fig:Trends_in_TC}, both air and vessel shipping exhibit a downward trend in overall transport costs since 1974, by \textbf{ACTUALISER LES CHIFFRES -2.1\% per year for mean air transport costs and -2.0\% per year XXX JH à GD : STP, refaire tourner la regression sous-jacente. LP quand je prends les chiffres des tableaux B1 et B2 je ne retrouve pas les graphiques, par ex en air 5.3\% en 1974, sur le graphique quasi 6?} for mean vessel transport costs, implying a \textbf{50\% decrease in air and a 60\% decrease in vessel over the period ACTUALISER, je trouve 55\% environ dans les deux modes, 2.3/5.3 et 4.1/8.9}.\footnote{One may be puzzled by the high magnitude of estimates for the beginning of the period (until 1980 approximately) for vessel transport.
\cite{hummels2007} finds similar outcomes on tramp prices indexes, and suggests the oil shock as a likely culprit, in a context where technological progress was quicker in aviation than in vessel, allowing a better dampening of oil shocks on air freight rates.
In a related manner, one may worry that the strong decrease in transport costs documented in Figure \ref{fig:Trends_in_TC} springs from high oil-shock-related transport costs in 1974. However, computing the time trends from 1980 does not dramatically change the picture.
The yearly trend from 1980 is -2\% for mean air transport costs and -1.6\% for mean vessel transport costs.
We thus choose to exploit the whole time dimension of our database by taking 1974 as starting date of our time-trend analysis.} Using US data, \cite{Hummels_1999} found that overall transport cost declined from 6\% to 4\% of the import value between 1974 and 1996.
For the same years, we obtain a total decrease from 5.3\% to 3\% in terms of the export price on average for air shipping, and from 8.9\% to 4.6\% for ocean shipping. Overall, our results display trends confirm and extend those reported by \cite{Hummels_1999} up to the very recent years.\smallskip

@@

Current data are available at the 10-digit level for products (HS10) for some specific years. The results reported here rely on exploiting data over the years 1997-1999 and 2001-2019.\footnote{Theoretically, they should be available from 1989, which is already smaller than our full sample starting in 1974. Because of the COVID situation, it was only possible to get access to the years 1997-1999 and 2001-2019.} \textbf{faut-il dire que le sample 10-3 n'est pas exactement le meme que nos baseline results et qu'on refait tourner le 5-3 sur le meme sample exactement?}

Yet, as Table \ref{tab:baseline10} and 	Figure \ref{fig:robustness_to_agregation} show, the results are similar when using 10-digit product and 5-digit products.

\begin{table}[htbp]
	\centering
	\caption{Transport costs estimates: Robustness to aggregation} \vspace{5mm} \label{tab:baseline10}
	\input{Table_baseline10_reshaped.tex}
	\begin{tablenotes}
		\scriptsize
		\item Statistics for 1997-1999 and 2002-2019
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
        \item Transport costs expressed in \% of the fas price (except for $\widehat{t}$ expressed in USD.
		%\item \textbf{Model (A): With ad-valorem transport costs only}
		\item \textbf{Model (B): With additive and ad-valorem transport costs}
	\end{tablenotes}
\end{table}

\textbf{JE NE COMPRENDS PAS LES RESULTATS EN VESSEL, 5-3 same sample as 10-3, PB? c'est un peu court comme commentaire, la comparison en air montre que la part des additifs est tout de meme plus faible, quasiment divisee par 2... A REPRENDRE JE PENSE}

\begin{figure}[htbp]
	\caption{Transport cost time trends: Robustness to aggregation}
	\label{fig:robustness_to_agregation}
	\begin{center}
		\includegraphics[height=8cm]{scatter_chronology_baseline_baseline10.png}
	\end{center}
\end{figure}

@@

Based on the above results, we provide a decomposition of the transport costs trends between the trade composition effects and the ``pure'' transport costs time trends, which explicitly takes into account the varying share of additive costs over time, country partner and product.\footnote{See Appendix \ref{app:compare_Hummels} for a detailed exposition of our method and a comparison with Hummel's (2007) methodology.} An important contribution of the paper is to show the crucial role of this (empirically relevant) assumption, as it notably modifies the conclusions relative to the role of trade composition effects.
We start with the presentation of our estimation strategy before turning to the results.\smallskip

@@

In this section, we explore the implications of our empirical results on theoretical grounds. While the whole bulk of the trade literature investigates the role of trade costs modelled as ad-valorem costs (e.g., iceberg trade costs), not much is said about the role of the additive component. One potential explanation is the lack of empirical estimates about the size of additive costs. Our results may thus usefully palliate this limitation. Specifically, we make use of our empirical results to investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019, contrasting two cases: When this reduction is achieved through a combined reduction in the ad-valorem and the additive
components (as quantified by our empirical model) or solely through the ad-valorem cost (as standardly modelled in New Trade models). To this aim, we embed additive costs in the canonical M\'{e}litz (2003) model.\smallskip

\cite{Irrazabal_2015}, \cite{sorensen2014} and \cite{Lashkaripour_JIE2020} have preceded us on this issue. We differentiate from them in the following way. \cite{sorensen2014} explores the welfare effects of a trade costs reduction depending on whether they are either fully ad-valorem or fully additive on analytical grounds. In contrast, we provide a quantification of such welfare gains, as in \cite{Irrazabal_2015} or \cite{Lashkaripour_JIE2020}. In a partial-equilibrium model with perfect competition, \cite{Lashkaripour_JIE2020} obtains that welfare gains are not substantially different whether the transport cost decrease implies an additive component or not. This stands in contrast with the conclusion reached by \cite{sorensen2014} (analytically) and \cite{Irrazabal_2015} (quantitatively) in M\'{e}litz' type models. Anticipating on our results, we also share the result, that the transport cost reduction implies substantially larger welfare gains when they are achieved through a reduction in the additive component. As first explanation, it should be noted that, in \cite{Lashkaripour_JIE2020}'s paper, the case with additive costs relies on a share of additive costs that remains negligible. In this context, one might expect that whether additive costs are present or not makes little difference. As underlined by \cite{Lashkaripour_JIE2020}, a second explanation may rely on the modeling framework. While \cite{Lashkaripour_JIE2020} models a perfectly competitive model, we as in \cite{sorensen2014} and \cite{Irrazabal_2015} adopt a model with monopolistic competition and firm selection \`{a} la \cite{melitz} or \cite{chaney2008}. In this setting, we show that additive costs do modify the selection of firms on both the domestic and the export markets, e.g the extensive margin of trade, whose role in the welfare gains of trade liberalization lies at the heart of the New Trade models  \`{a} la \cite{melitz}. Put differently, leaving aside the selection issue leads to underestimate the welfare gains that can be achieved by a reduction in the additive component of transport costs.

@@

In line with the literature, we find that trade liberalization induces welfare gains whatever the transport mode (and the associated magnitude of the transport costs decrease). The originality of our results rather dwells on comparing the welfare gains depending on the type of cost reduction. On that side, the welfare gains are higher when the trade cost reduction occurs through a decrease in the additive component. This is consistent with the analytical results of \cite{sorensen2014}, in a different exercise of trade liberalization though. \footnote{\cite{sorensen2014} compares the welfare effect of a trade costs reduction depending whether it is exclusively ad-valorem or exclusively additive, the comparison between both trade cost decreases being a criterion of equal impact on trade openness. Our quantitative model offers a more general and flexible set-up, as we can virtually consider all cases of trade liberalization. Based on our empirical estimates, we compare the effects of the same decrease in overall transport costs depending on 1) whether additive costs are present or not, and 2) when they are present, assuming that the trade cost decrease is achieved by a reduction of both additive and ad-valorem components.} Quantitatively, the welfare gains are sizeable. In our preferred scenario, the reduction variable transport costs generates a relative welfare gain higher by around 1.1 percentage point when such a reduction occurs through the additive component (which accounts for 50 to 60\% of the total cost decrease, depending on the transport mode), rather than when it realizes through a decrease in iceberg costs only (Table \ref{tab:resultats_modele}, panel (1), Column (B) vs (A) for Air, (D) vs (C) for Vessel). \cite{Irrazabal_2015} also quantify the welfare gains of a trade cost decrease in presence of additive costs. If we share a similar conclusion regarding the importance of additive costs, our empirical analysis allows us to simulate the effects of the reduction in transport costs actually observed in the data over the period 1974-2019, in all their dimensions (additive and ad-valorem). \smallskip

@@

This paper assesses the magnitude and the role of additive international transport costs. Empirically, we exploit the differences between the import and the export prices taken from the US import database over 1974-2019, to estimate the two components (additive and ad-valorem) of transport costs, by transport mode (air or ocean). We find that additive costs are quantitatively sizable: On average over the period, they amount to 2.8\% of the export price unit values for ocean shipping, and 1.7\% for air transport, accounting for 30\% and 45\% of total transport costs in air and maritime transport respectively.

To what extent should we care about additive costs? Our paper addresses this question through two different angles. First, we show the importance of integrating the additive component in accounting for the time trend of international transport costs observed over 1974-2019. Allowing for a varying share of additive costs in the product/country/time dimension, we find that the decrease of international transport costs observed in the data is mostly attributable to a reduction in the \textit{pure} transport costs, with trade pattern composition effects playing a small role. If anything, trade composition effects have contributed to amplifying the reduction in the pure transport costs in maritime transport.

Second, we revisit the question of the welfare gains from trade liberalisation to shed light on the role of additive costs on this issue. To this aim, we amend the canonical M\'{e}litz (2003) model with additive costs. Relying on our empirical estimates of transport
costs over 1974-2019, our preferred scenario shows an extra welfare gain by around 1.2
percentage point when the transport cost decrease encompasses a reduction in its additive
component (as we document empirically) relative to a pure ad-valorem reduction. In both aspects, our results highlight the importance of the additive component in accounting for international transport costs.

Our results could be extended in two main ways.
On the empirical side, one may want to go deeper into the structural determinants of (pure) transport costs - i.e.
identify the respective roles of handling costs, insurance and freight at the root of the gap between export and import prices.
On the theoretical side, our results call for exploring the role of additive costs in shaping international trade flows in richer New Trade models than the canonical M\'{e}litz model used so far, and in affecting the international transmission of business cycles.
This is left for further research.
